---
title: "Gunboat Diplomacy"
subtitle: "Political Bias, Trade Policy, and War"
author: Brendan Cooley
date: "19 January 2019"
output: 
  revealjs::revealjs_presentation:
    template: "cooley-reveal.html"
    css: "css/cooley-reveal.css"
    transition: none
    reveal_options:
      slideNumber: true
---

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
# TODO cite background image: Charles Severin (American lithographer, born between 1808-1820; died ca. 1860). 1853 (creation). The American Expedition, The American Expedition, Under Commodore Perry, Landing in Japan, July 14, 1853, Overall view. visual works; prints (visual works); planographic prints; lithographs. https://library.artstor.org/asset/SS35100_35100_35234600.
```

## The Modern Economic Peace

```{r emp_wars, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE, fig.align="center", fig.height=6}

source("figs/emp_wars.R")

polityDensity <- polityDensity + theme(plot.title = element_blank())

polityDensity + empty + main + tradeIntDensity + polityRail + empty + plot_layout(ncol=2, widths=c(8,1), heights=c(1,15,2))

```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

