---
title: "Gunboat Diplomacy"
subtitle: "Political Bias, Trade Policy, and War"
date: "13 March 2019"
author: Brendan Cooley
position: Ph.D. Candidate
institution: Princeton University
email: "bcooley (at) princeton.edu"

bibliography: /Users/brendancooley/Dropbox (Princeton)/References/library.bib
biblio-style: apsr

backgroundTitle: "figs/perry.jpg"

revealjs-url: "index_files/reveal.js-3.8.0"

output:
  revealjs::revealjs_presentation:
    template: "css/cooley-reveal.html"
    css: "css/cooley-reveal-Alegreya.css"
    backgroundTransition: none
    transition: none
    self_contained: false
    # reveal_plugins: ["notes"]
    lib_dir: index_files
    revealjs-url: "index_files/reveal.js-3.8.0"
    reveal_options:
      slideNumber: false
      progress: false
      controls: true
---

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

helperPath <- "source/R/"
helperFiles <- list.files(helperPath)
for (i in helperFiles) {
  source(paste0(helperPath, i))
}

libs <- c('tidyverse', "latex2exp", "countrycode", "ggrepel", "ggpubr", "patchwork")
ipak(libs)

# TODO: speaker notes don't work with incremental reveal
# TODO: nested bulleted lists disappear after compilation, fine when knitting
# TODO: need to manually add fragments on first vertical slide (. . .) doesn't work

Akappa <- "NA"

if (file.exists('references.RData')) load('references.RData')

# get helper functions
source('figs/source.R')

# get params
source('figs/params.R')

```

# Trade and War: Received Wisdom {id="intro"}

<div class="fragment">

> "Free trade serves the cause of economic progress, and it serves the cause of world peace." <br/> $\qquad$ -- Ronald Reagan, Nov. 1982

<center><hr width="50%"></center>

</div>
<div class="fragment">

> "Commercial relations draw states into a web of mutual self-interest that constrains them from using force against one another." <br/> $\qquad$ -- Oneal and Russett (1999)

<center><hr width="50%"></center>

<hr style="height:1em; visibility:hidden;" />

</div>
<div class="fragment">

**Dominant Paradigm:** Trade mediates *preexisting* conflicts of interest

- Conflicts of interest: territorial, ideological, otherwise
- War disrupts trade, imposes *opportunity costs*

</div>

## Gunboat Diplomacy

**Examples**

- Perry Expeditions (1852-1854)
- Opium Wars (1839-1842; 1856-1860)
- Euromaidan and War in Donbass (2014-present)

. . .

**Commercial Policy Objectives**

- Governments are mercantilistic, desiring
    - Some degree of trade protection at home
    - Trade liberalization or *market access* abroad

. . .

**Market Access Externalities**

- Protectionist barriers *shift profits* from foreign to home firms
- Trade policy generates conflicts of interest between mercantilist governments

. . .

**International Anarchy**

- Efforts to address externalities can include threats, displays, and uses of military force
    + Bargaining critique [@Fearon1995]: absence of war does not imply absence of coercion

## A Theory of Trade Policy in the Shadow of Power

**Model**

- "New Trade" International Economy
    + @Krugman1980, @Venables1987; @Ossa2012
- Mercantilist/Politically-Biased Governments
    + @Grossman1994, @BuenodeMesquita2003, @Jackson2007
    + *Liberal* governments afford consumers greater influence over the trade policymaking process
- Ultimatum Coercive Bargaining
    + @Fearon1995, @Fey2019

. . .

**Results**

- Trade and Conflict
    + Liberal governments experience smaller conflicts of interest (Proposition `r Pgamma`)
    + "" fight war less frequently (Proposition `r Pwar`)
    + "" trade more when peace prevails (Proposition `r PeqTrade`)

. . .

- Trade Policy in the Shadow of Power
    + Trade policies reflect balance of military power, powerful countries more protectionist in equilibrium (Proposition `r PeqTau`)

. . .

<hr style="height:1em; visibility:hidden;" />

<p class="center">*Trade and peace are correlated in equilibrium, but not because trade causes peace*</p>

## Literature {id="literature"}

- Trade and War
    + @Angell1911,  @Polachek1980, @Gowa1993, @Morrow1999b, @Barbieri1999, @Mansfield2000a, @Gartzke2001, @Mcdonald2004, @Mcdonald2007, @Gartzke2007, @Benson2007, @Philippe2008, @Hegre2010, @Copeland2014
- Power and Trade
    + @Hirschman1945, @Krasner1976, @Gourevitch1978, @Pollins1989a, @Pollins1989b, @Antras2011, @Chatagnier2015, @Carroll2018
- Political Economy of Trade Policy
    + @Mayer1984, @Grossman1994, @Kono2008, @Gawande2009, @Ossa2011, @Ossa2012, @Ossa2014
- Democracy and Trade
    + @Mansfield2000b, @Milner2005
- Democracy and War
    + @Lake1992, @Snyder1993, @Oneal1997, @Schultz1998, @Oneal1999, @Schultz2001, @Fearon2008, @CoeND

## The Commercial-Democratic Peace {id="comDemPeace"}

```{r emp_wars, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center", fig.height=6, cache=TRUE}

source("figs/emp_wars.R")

polityDensity <- polityDensity + theme(plot.title = element_blank())

polityDensity + empty + main + tradeIntDensity + polityRail + empty + plot_layout(ncol=2, widths=c(8,1), heights=c(1,15,2))

rm(tradeM)
rm(tradeF)
rm(tradeUF)
rm(wars)

```

## Trade and War Onset {id="tradeRD"}

```{r tradeRD, echo=FALSE, warning=FALSE, message=FALSE, fig.cap = "\\label{fig:tradeRD}", fig.height=5.5, dpi=300, cache=TRUE}

source("figs/emp_wars.R")

tradeRDplot

rm(tradeM)
rm(tradeF)
rm(tradeUF)
rm(wars)

```

# Model Overview {id="overview"}

- Two goverments ($i, j$), ultimatum bargaining over tariffs
- Payoffs depend on international economic effects of tariffs and latent protectionism of governments

<div class="fragment">

**International Economy**

- Mass of firms in each country ("industry"), produce differentiated varieties
    + Outside sector ("agriculture")
- Profit-shifting motivations for tariffs

</div>
<div class="fragment">

**Domestic Political Economy**

- Governments maximize weighted combination of consumer welfare and industry profits
    + Variation in preferences (open-protectionist)
- Tension in trade policy
    + Tariffs increase profits
    + Decrease consumer welfare

</div>
<div class="fragment">

**International Bargaining**

- Threat point: regime change
    + Power: probability government wins a war for regime change
    + Victorious governments impose new preferences on vanquished governments
- Ultimatum offer: pair of tariffs
    + Private information over wars costs $\implies$ war in equilibrium

</div>

## Comparative Statics {.centercontent}

- $\Delta$ Preferences $\rightarrow \text{Pr} (\text{war})$
- $\Delta$ Preferences $\rightarrow$ protection, trade flows
- $\Delta$ Military power $\rightarrow$ protection, trade flows

## Bargaining Environment

<div class="fragment">

- "Home" ($i$) government makes TIOLI trade policy offer to "foreign" ($j$) $\widetilde{\boldsymbol{\tau}} = \left\{ \widetilde{\tau}_i, \widetilde{\tau}_j \right\} \in [1, \bar{\tau}]^2$
- Foreign accepts or rejects
- Information about $j$'s costs of war ($c_j$) held privately, distributed uniform on $[\ubar{c}_j, \bar{c}_j]$

</div>
<div class="fragment">

**Definition `r beq`:** A subgame perfect *bargaining equilibrium* is pair of strategies, $\widetilde{\boldsymbol{\tau}}^\star(a_i, c_i)$ and $\omega^\star(\widetilde{\boldsymbol{\tau}}; a_j, c_j)$ such that
$$
\omega^\star(\widetilde{\boldsymbol{\tau}}; a_j, c_j, \rho) = \text{argmax}_{\omega \in \left\{\text{accept}, \text{war} \right\}} \widetilde{G}_j \left(\widetilde{\boldsymbol{\tau}}, \omega; a_j, c_j, \rho \right)
$$
and
$$
\widetilde{\boldsymbol{\tau}}^\star(a_i, c_i, \rho) \in \text{argmax}_{\boldsymbol{\tau} \in [1, \overline{\tau}]^2} \mathbb{E}_{f(c_j)} \left[ \widetilde{G}_i \left(\widetilde{\boldsymbol{\tau}}, \omega^\star(\widetilde{\boldsymbol{\tau}}; a_j, c_j, \rho); a_i, c_i, \rho \right) \right]
$$

- $\widetilde{G}$ government utility
- $\rho \in [0, 1]$ probability $i$ wins war (military strength)

</div>
<div class="fragment">

**Assumption `r AwCosts`:** `r AwCostsText`

</div>

# Economy (I) {id="economy"}

<div class="fragment">

**Primitives**

- Factor endowments: $L_i = L_j = L$
- Income: $I_i = w_i L_i + r_i(\tau_i)$
- Mass of industrial firms indexed $\nu_i$
    + $\int_{\nu_i} d \nu_i = \int_{\nu_j} d \nu_j = 1$
    + *No entry $\implies$ positive profits in equilibrium* (short-run)

</div>
<div class="fragment">

**Consumption**

- Agricultural consumption: $Y_i$
- Cobb-Douglas upper-level preferences

\begin{equation} \label{eq:cMax}
\begin{split}
\max_{X_i, Y_i} & \quad X_i^\alpha Y_i^{1 - \alpha} \\
\text{subject to} & \quad P_i X_i + Y_i \leq w_i L
\end{split}
\end{equation}

</div>
<div class="fragment">

## Economy (II)

**Consumption (Continued)**

- Industrial consumption: $P_i X_i = \alpha I_i$
- Constant elasticity of substitution (CES) preferences over industrial varieties

\begin{equation} \label{eq:CES}
X_i = \left( \int_{\nu_i} x_{ii}(\nu_i)^{\frac{\sigma - 1}{\sigma}} d \nu_i + \int_{\nu_j} x_{ij}(\nu_j)^{\frac{\sigma - 1}{\sigma}} d \nu_j \right)^{\frac{\sigma}{\sigma - 1}}
\end{equation}

\begin{equation} \label{eq:P}
P_i = \left( \int_{\nu_i} p_{ii}(\nu_i)^{1-\sigma} d \nu_i + \int_{\nu_j} p_{ij}(\nu_j)^{1-\sigma} d \nu_j \right)^{\frac{1}{1 - \sigma}}
\end{equation}

- Indirect utility

\begin{equation} \label{eq:V}
V_i(P_i) = \alpha^\alpha (1 - \alpha)^{1 - \alpha} \frac{I_i}{P_i^\alpha}
\end{equation}

## Economy (III)

**Tariffs and Prices**

$$
p_{ij} = \tau_i p_j(\nu_j)
$$

- $p_{ij}$ - price in country $i$ of industrial goods produced in $j$ 
- $\tau_i - 1$ - ad valorem tariff imposed by $i$ on industrial imports from $j$

. . .

**Production**

\begin{equation} \label{eq:Pi}
\begin{split}
\max_{p_i(\nu_i)} & \quad \Pi_i \left( p_i(\nu_i) \right) = \left( p_i(\nu_i) - w_i \right) \left( x_{ii}^\star(\nu_i) + x_{ji}^\star(\nu_i) \right) \\
\text{subject to} & \quad x_{ii}^\star(\nu_i) = p_i(\nu_i)^{-\sigma} P_i^{\sigma - 1} \alpha I_i \\
& \quad x_{ji}^\star(\nu_i) = (\tau_j p_i(\nu_i))^{-\sigma} P_j^{\sigma - 1} \alpha I_i
\end{split}
\end{equation}

- $x_{ii}^\star(\nu_i)$ - domestic consumption of variety $\nu_i$
- $x_{ji}^\star(\nu_i)$ - exports of variety $\nu_i$

. . .

**Tariff Revenue**

\begin{equation} \label{eq:revenue}
r_i(\tau_i) = (\tau_i - 1) p_j x_{ij}^\star(\tau_i p_j)
\end{equation}

- $x_{ij}^\star(\tau_i p_j)$ - total industrial imports

## Economic Equilibrium

- $\bm{w} = \left\{ w_i^x, w_i^y \right\}_{i \in \left\{ i, j \right\} }$ 
- $\bm{L} = \left\{ L_i^x, L_i^y \right\}_{ i \in \left\{ i, j \right\} }$

. . . 

**Definition `r eeqD`:** `r DeeqText`

. . . 

**Assumption `r Aalpha`:** `r AalphaText`

. . . 

**Proposition `r eeqP`:** `r PeeqText`

. . .

- Wages constant, positive tariffs...
    + raise revenue
    + increase industry profits
    + *do not manipulate terms of trade* [@Bagwell1999]

# Domestic Political Economy {id="dpe"}

<div class="fragment">

**Government Preferences (I)**

<hr style="height:1em; visibility:hidden;" />

\begin{equation} \label{eq:G}
G_i(\bm{\tau} | a_i) = a_i V_i(\tau_i) + \Pi_i(\tau_i, \tau_j)
\end{equation}

<hr style="height:1em; visibility:hidden;" />

- $V_i(\tau_i)$ - consumer welfare
- $\Pi_i(\tau_i, \tau_j)$ - firm profits
    - increasing in $\tau_i$, decreasing in $\tau_j$

<p class="center">*$a_i$ is measure of government's sensitivity to interests of consumers*</p>

</div>
<div class="fragment">

**Assumption `r Aa`:** `r AaText`

</div>
<div class="fragment">

**Lemma `r Lqccv`:** `r LqccvText`

</div>

## Government Preferences (II)

```{r G1, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, dpi=300}

source("figs/G.R")

Gplot1

```

## Government Preferences (II)

```{r G2, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, dpi=300}

Gplot2

```

## Government Preferences (II) {id="objective"}

```{r G3, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, dpi=300}

Gplot3

```

## Government Preferences (III)

```{r iso1, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, dpi=300}

source("figs/iso.R")

isoPlot1

```

## Government Preferences (III) {id="iso"}

```{r iso2, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, dpi=300}

isoPlot2

```

## Government Preferences (IV) {.centercontent}

- **Lemma `r tauj`:** `r LtaujText`
- **Lemma `r taui`:** `r LtauiText`

## Noncooperative Equilibrium (I) {.centercontent id="nce"}

**Definition `r nceq`:** `r DnceqText`

## Noncooperative Equilibrium (II)

```{r br, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, dpi=300}

brPlot

```

# Conflicts of Interest and Regime Change (I) {id="regimeChange"}

<div class="fragment">

**Optimal Puppet Regimes**

$$
\max_{a \in (\ubar{a}, \bar{a}]} G_i( \tau_i^\star(a_i), \tau_j^\star(a) | a_i )
$$

- When a government wins a war, it earns the right to replace the vanquished government with a "puppet" that prefers lower barriers to trade
- Losing governments have puppet's policies imposed on them

</div>
<div class="fragment">

**War Outcomes**

\begin{equation*} \label{eq:Gbar}
\bar{G}_i(a_i) = G_i(\tau_i^\star(a_i), \tau_j^\star(\bar{a}); a_i)
\end{equation*}

\begin{equation*} \label{eq:Gubar}
\ubar{G}_i(a_i, a_j) = G_i(\tau_i^\star(\bar{a}), \tau_j^\star(a_j); a_i)
\end{equation*}

</div>
<div class="fragment">

**Conflicts of Interest**

\begin{equation} \label{eq:Gamma}
\Gamma_i(a_i, a_j) = \overline{G}_i(a_i) - \underline{G}_i(a_i, a_j)
\end{equation}

- Utility difference between (costlessly) winning a war for regime change and being replaced by a puppet

</div>

## Conflicts of Interest and Regime Change (II) {.centercontent}

**Proposition `r Pgamma`:** `r PgammaText`

## Bargaining Environment (I) {id="barEnv"}

```{r bar, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, dpi=300}

source("figs/bar.R")

barPlot

```

## Bargaining Environment (II)

**War Values**

\begin{align*}
\hat{G}_j(a_j, a_i) &= \underbrace{(1 - \rho) \bar{G}_j(a_j) + \rho \ubar{G}_j(a_j, a_i)}_{W_j(a_j, a_i)} - c_j \\ 
&= (1 - \rho) \Gamma_j(a_j, a_i) + \ubar{G}_j(a_j, a_i) - c_j
\end{align*}

- $(1 - \rho)$ - probability $j$ wins the war

. . .

**Lemma `r omegaStar`:** `r LomegaStarText`

# Results {id="results"}

<div class="fragment">

**Liberal Peace**

**Lemma `r LtauCorner`:** `r LtauCornerText`

</div>
<div class="fragment">

**Lemma `r LaEpsilon` (Zone of Peace):** `r LaEpsilonText`

</div>

## Liberal Peace {.centercontent}

**Proposition `r Pwar` (Liberal Peace):** `r PwarText`

## Power and Protection (I)

**Probability of War**

\begin{equation} \label{eq:prwar}
\begin{split}
\text{Pr} \left\{ c_j \leq W_j(a_j, a_i) - G_j(\tilde{\bm{\tau}}; a_j) | \tilde{\bm{\tau}}, a_i, a_j \right\} = F \left( W_j(a_j, a_i) - G_j(\tilde{\bm{\tau}}; a_j)  \right)
\end{split}
\end{equation}

. . .

**War Value ($i$)**

$$
\hat{G}_i(a_i, a_j) = \rho \Gamma_i(a_i, a_j) + \ubar{G}_i(a_i, a_j) - c_i
$$

. . . 

**Induced Objective Function**

\begin{equation} \label{eq:Gtildei}
\begin{split}
\tilde{G}_i \left( \tilde{\bm{\tau}}; a_i, c_i, \rho \right) = \underbrace{\left( 1 - F \left( W_j(a_j, a_i) - G_j( \tilde{\bm{\tau}}; a_j ) \right) \right) \left( G_i( \tilde{\bm{\tau}}; a_i ) \right)}_{\neg \text{war}} + \\
\underbrace{F \left( W_j(a_j, a_i) - G_j(\tilde{\bm{\tau}}; a_j) \right) \left( \hat{G}_i(a_i, a_j) \right)}_{\text{war}}
\end{split}
\end{equation}

## Power and Protection (II) {.centercontent}

**Proposition `r PeqTau` (Power and Protection):** `r PeqTauText`

## Liberal Trade (I)

```{r bar2, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, dpi=300}

source("figs/bar.R")

barPlot

```

## Liberal Trade (II) {.centercontent}

**Proposition `r PeqTrade` (Liberal Trade):** `r PeqTradeText`

# Implications {id="implications"}

**Preferences, Institutions, and the Democratic Peace**

<div class="fragment">

- Hypothesis: Democracies more liberal in trade policy preferences than autocracies
    + Democratic political institutions and consumer influence over policymaking [@Mayer1984; @Grossman1996; @Milner2005]

</div>
<div class="fragment">

- Conclusion: Democracies trade more, fight less
    + Democratic peace: @Oneal1999, @Reiter2017

</div>
<div class="fragment">

**Shadow of Power in International Political Economy**

- Equilibrium trade policies balance
    + Domestic political interests
    + Foreign military constraints

</div>
<div class="fragment">

- Trade policies *are not* a sufficient statistic for government preferences
    + @Goldberg1999; @Mitra2006; @Gawande2009; @Gawande2012; @Ossa2014; @Gawande2015

</div>

## Conclusion

<hr style="height:6em; visibility:hidden;" />

**Conflicts of Interest versus Bargaining Failures**

- *Given* a conflict of interest, what prevents peaceful settlement? [@Fearon1995]
- What do governments want? and why do their objectives bring them into conflict with one another? [@Moravcsik1997]

# Thank You  {.aligncenter}

[brendancooley.com](http://brendancooley.com)

[bcooley@princeton.edu](bcooley@princeton.edu)

<small>**Title Slide Image Credit:** Charles Severin (American lithographer, born between 1808-1820; died ca. 1860). 1853 (creation). The American Expedition, Under Commodore Perry, Landing in Japan, July 14, 1853, Overall view. visual works; prints (visual works); planographic prints; lithographs. https://library.artstor.org/asset/SS35100_35100_35234600</small>

# Table of Contents {id="toc"}



<div id="left">

**Sections**

1. <a href="#/intro">Introduction</a>
2. <a href="#/overview">Model Overview</a>
3. <a href="#/economy">International Economy</a>
4. <a href="#/dpe">Domestic Political Economy</a>
5. <a href="#/regimeChange">Regime Change</a>
6. <a href="#/results">Results</a>
7. <a href="#/implications">Discussion</a>
</div>

<div id="right">

**Quick Links**

1. <a href="#/comDemPeace">Commercial-Democratic Peace</a>
2. <a href="#/tradeRD">Trade and War</a>
3. <a href="#/objective">Objective Function</a>
4. <a href="#/iso">Iso-Welfare Curves</a>
5. <a href="#/barEnv">Bargaining Environment</a>
</div>

<!-- hide references -->
<hr style="height:30em; visibility:hidden;" />