---
title: "Gunboat Diplomacy"
subtitle: "Political Bias, Trade Policy, and War"
author: Brendan Cooley
date: "13 March 2019"

bibliography: /Users/brendancooley/Dropbox (Princeton)/References/library.bib
biblio-style: apsr

output: 
  revealjs::revealjs_presentation:
    template: "cooley-reveal.html"
    css: "css/cooley-reveal.css"
    backgroundTransition: none
    transition: none
    self_contained: true
    # reveal_plugins: ["notes"]
    lib_dir: index_files
    reveal_options:
      slideNumber: true
      progress: false
      controls: false
    includes:
      after_body: plugins.html
---

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
# TODO: vertical slides currently not behaving
# TODO: speaker notes don't work with incremental reveal
# TODO: nested bulleted lists disappear after compilation, fine when knitting


if (file.exists('references.RData')) load('references.RData')

# get helper functions
source('figs/source.R')

# get params
source('figs/params.R')

```

## Trade and War: Received Wisdom {id="intro"}

> "Free trade serves the cause of economic progress, and it serves the cause of world peace." -- Ronald Reagan, Nov. 1982

<center><hr width="50%"></center>

. . . 

> "Commercial relations draw states into a web of mutual self-interest that constrains them from using force against one another." -- Oneal and Russett (1999)

<center><hr width="50%"></center>

<hr style="height:1em; visibility:hidden;" />

. . . 

**Dominant Paradigm:** Trade mediates *preexisting* conflicts of interest

- Conflicts of interest: territorial, ideological, otherwise
- War disrupts trade, imposes *opportunity costs*

<a href="#/tradeRD" style="float: right;">Trade and War Onset</a>

## Gunboat Diplomacy

**Examples**

- Perry Expeditions (1852-1854)
- Opium Wars (1839-1842; 1856-1860)
- Euromaidan and War in Donbass (2014-present)

. . . 

**Commercial Policy Objectives**

- Governments are mercantilistic, desiring
    - Some degree of trade protection at home
    - Trade liberalization or *market access* abroad

. . . 

**Market Access Externalities**

- Protectionist barriers *shift profits* from foreign to home firms
- Trade policy generates conflicts of interest between mercantilist governments

. . . 

**International Anarchy**

- Efforts to address externalities can include threats, displays, and uses of military force
    + Bargaining critique [@Fearon1995]: absence of war does not imply absence of coercion 

## A Theory of Trade Policy in the Shadow of Power {id="overview"}

**Model**

- "New Trade" International Economy
    + @Krugman1980, @Venables1987; @Ossa2012
- Mercantilist/Politically-biased Governments
    + @Grossman1994, @BuenodeMesquita2003, @Jackson2007
- Ultimatum Coercive Bargaining
    + @Fearon1995

. . . 

**Results**

- Trade and Conflict
    + *Liberal* governments experience smaller conflicts of interest (Proposition `r Pgamma`)
    + "" fight war less frequently (Proposition `r Pwar`)
    + "" trade more when peace prevails (Proposition `r PeqTrade`)

. . .

- Trade Policy in the Shadow of Power
    + Trade policies reflect balance of military power, powerful countries more protectionist in equilibrium (Proposition `r PeqTau`)

. . . 

<p class="center">*Trade and peace are correlated, but not because trade causes peace*</p>

<a href="#/literature" style="float: right;">Literature</a>

## Bargaining Environment

- "Home" ($i$) government makes TIOLI trade policy offer to "foreign" ($j$) $\widetilde{\boldsymbol{\tau}} = \left\{ \widetilde{\tau}_i, \widetilde{\tau}_j \right\}$

. . .

- Foreign accepts or rejects
    + Rejection results in war for *regime change*

. . .

- Information about $j$'s costs of war ($c_j$) held privately, distributed  $f(c_j)$

. . . 

<hr style="height:1em; visibility:hidden;" />

<center><hr width="50%"></center>

**Definition `r beq`:** A subgame perfect *bargaining equilibrium* is pair of strategies, $\widetilde{\boldsymbol{\tau}}^\star(a_i, c_i)$ and $\omega^\star(\widetilde{\boldsymbol{\tau}}; a_j, c_j)$ such that
$$
\omega^\star(\widetilde{\boldsymbol{\tau}}; a_j, c_j, \rho) = \text{argmax}_{\omega \in \left\{\text{accept}, \text{war} \right\}} \widetilde{G} \left(\widetilde{\boldsymbol{\tau}}, \omega; a_j, c_j; \rho \right)
$$
and
$$
\widetilde{\boldsymbol{\tau}}^\star(a_i, c_i, \rho) \in \text{argmax}_{\boldsymbol{\tau} \in [1, \overline{\tau}]^2} \mathbb{E}_{f(c_j)} \left[ \widetilde{G} \left(\widetilde{\boldsymbol{\tau}}, \omega^\star(\widetilde{\boldsymbol{\tau}}; a_j, c_j, \rho); a_i, c_i; \rho \right) \right]
$$

<hr style="height:1em; visibility:hidden;" />

<center><hr width="50%"></center>

<hr style="height:1em; visibility:hidden;" />

- $\widetilde{G}$ government utility
- $\rho$ probability $i$ wins war (military strength)

## Domestic Political Economy {id="dpe"}

**Government Preferences**

<hr style="height:1em; visibility:hidden;" />

\begin{equation} \label{eq:G}
G_i(\tau_i, \tau_j | a_i) = a_i V_i^x(\tau_i) + \Pi_i(\tau_i, \tau_j) + r_i(\tau_i)
\end{equation}

<hr style="height:1em; visibility:hidden;" />

- $V_i^x(\tau_i)$ - consumer welfare
    - decreasing in $\tau_i$
- $\Pi_i(\tau_i, \tau_j)$ - firm profits
    - increasing in $\tau_i$, decreasing in $\tau_j$
- $r_i(\tau_i)$ - tariff revenue
    - non-monotonic in $\tau_i$

<p class="center">*$a_i$ is measure of government's sensitivity to interests of consumers*</p>

<a href="#/assumptions" style="float: right;">Assumptions</a>

. . . 

**International Economy**

- Representative consumer and $n$ firms in each economy, monopolistic competition
    - Krugman 1980, Venables 1987, Ossa 2012

<a href="#/economy" style="float: right;">Economy</a>

## Government Preferences I

```{r G, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, dpi=300, cache=TRUE}

source("figs/G.R")

GPlot

```

## Government Preferences II {id="iso"}

```{r iso, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, dpi=300, cache=TRUE}

source("figs/iso.R")

isoPlot

```

<a href="#/Gprefs" style="float: right;">Results</a>

## Noncooperative Equilibrium {id="nce"}

```{r br, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, dpi=300, cache=TRUE}

brPlot

```

<a href="#/nceDef" style="float: right;">Definition</a>

## Conflicts of Interest and Regime Change

**Optimal Puppet Regimes**

- When a government wins a war, it earns the right to replace the vanquished government with a "puppet" that prefers lower barriers to trade

<hr style="height:1em; visibility:hidden;" />
$$
\max_{a \in (0, \overline{a}]} G_i( \tau_i^\star(a_i), \tau_j^\star(a) | a_i )
$$
<hr style="height:1em; visibility:hidden;" />

- Losing governments have puppet's policies imposed on them

. . . 

**Conflicts of Interest**

- Utility difference between (costlessly) winning a war for regime change and being replaced by a puppet

<hr style="height:1em; visibility:hidden;" />

\begin{equation} \label{eq:Gamma}
\Gamma_i(a_i, a_j) = \overline{G}_i(a_i) - \underline{G}_i(a_i, a_j)
\end{equation}

. . . 

**Proposition `r Pgamma`:** `r PgammaText`

## Bargaining Environment {id="barEnv"}

```{r bar, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, dpi=300}

source("figs/bar.R")

barPlot

```

<a href="#/bargaining" style="float: right;">Bargaining</a>

## Results

<hr style="height:4em; visibility:hidden;" />

### Trade and War

**Proposition `r Pwar`:** `r PwarText`

. . . 

**Proposition `r PeqTrade`:** `r PeqTradeText`


## Results

<hr style="height:4em; visibility:hidden;" />

### Trade and War

**Proposition `r Pwar`:** `r PwarText`

**Proposition `r PeqTrade`:** `r PeqTradeText`

### Shadow of War and Trade Policy

**Proposition `r PeqTau`:** `r PeqTauText`

## Implications {id="implications"}

**Preferences, Institutions, and the Democratic Peace**

- Hypothesis: Democracies more liberal in trade policy preferences than autocracies 
    + Democratic political institutions and consumer influence over policymaking [@Mayer1984; @Grossman1996; @Milner2005]

. . . 

- Conclusion: Democracies trade more, fight less
    + Democratic peace: @Oneal1999, @Reiter2017

<p style="text-align: right;"><a href="#/comDemPeace">Commercial-Democratic Peace</a></p>

. . . 

**Shadow of Power in International Political Economy**

- Equilibrium trade policies balance
    + Domestic political interests
    + Foreign military constraints

. . . 

- Trade policies *are not* a sufficient statistic for government preferences
    + @Goldberg1999; @Mitra2006; @Gawande2009; @Gawande2012; @Ossa2014; @Gawande2015

## Conclusion

**Domestic Political Economy of War**

> "We shall invite the minority party to join us...in stopping partisan politics at the water's edge." -- Sen. Arthur Vandenberg, 4 October 1948

<center><hr width="50%"></center>

<hr style="height:1em; visibility:hidden;" />

- @Gerschenkron1943, @Williams1988, @Fordham1998, @Kleinberg2013, @Fordham2019

. . . 

**Conflicts of Interest versus Bargaining Failures**

- *Given* a conflict of interest, what prevents peaceful settlement? [@Fearon1995]
- What do governments want? and why do their objectives bring them into conflict with one another? [@Moravcsik1997]

## Thank You {.center}

[brendancooley.com](http://brendancooley.com)

[bcooley@princeton.edu](bcooley@princeton.edu)

<small>**Title Slide Image Credit:** Charles Severin (American lithographer, born between 1808-1820; died ca. 1860). 1853 (creation). The American Expedition, Under Commodore Perry, Landing in Japan, July 14, 1853, Overall view. visual works; prints (visual works); planographic prints; lithographs. https://library.artstor.org/asset/SS35100_35100_35234600</small>

## Trade and War Onset {id="tradeRD"}

```{r tradeRD, echo=FALSE, warning=FALSE, message=FALSE, fig.cap = "\\label{fig:tradeRD}", fig.height=6, dpi=300, cache=T}

source("figs/emp_wars.R")

tradeRDplot

```

<a href="#/intro" style="float: right;">Back</a>

## Literature {id="literature"}

- Trade and War
    + @Angell1911, @Polachek1980, @Gowa1993, @Morrow1999b, @Barbieri1999, @Mansfield2000a, @Gartzke2001, @Mcdonald2004, @Mcdonald2007, @Gartzke2007, @Benson2007, @Philippe2008, @Hegre2010, @Copeland2014
- Power and Trade
    + @Hirschman1945, @Krasner1976, @Gourevitch1978, @Pollins1989a, @Pollins1989b, @Antras2011, @Chatagnier2015, @Carroll2018
- Political Economy of Trade Policy
    + @Mayer1984, @Grossman1994, @Kono2008, @Gawande2009, @Ossa2011, @Ossa2012, @Ossa2014
- Democracy and Trade
    + @Mansfield2000b, @Milner2005
- Democracy and War
    + @Lake1992, @Snyder1993, @Oneal1997, @Schultz1998, @Oneal1999, @Schultz2001, @Fearon2008, @CoeND


<a href="#/overview" style="float: right;">Back</a>

## Assumptions {id="assumptions"}

<hr style="height:2em; visibility:hidden;" />

**Assumption `r Akappa`:** (costs of war are bounded) $c_i < \kappa$ where $\kappa$ is a postive constant defined in the Appendix.

**Assumption `r aAlpha`:** (agricultural sector sufficiently large)
<hr style="height:1em; visibility:hidden;" />
$$
\alpha < \frac{2}{3} \frac{\sigma}{\sigma - 1}
$$ 
<hr style="height:1em; visibility:hidden;" />

**Assumption `r aA`:** (governments are weak mercantilists) $a_i \in (0, \overline{a})$ with
<hr style="height:1em; visibility:hidden;" />
$$
\overline{a} = (2n)^{\frac{1}{1-\sigma}} \left( \frac{\sigma}{\sigma - 1} + \frac{1}{2} \right)
$$
<hr style="height:1em; visibility:hidden;" />

<a href="#/dpe" style="float: right;">Back</a>

## Economy {id="economy"}

**Consumption**

\begin{equation} \label{eq:cMax}
\begin{split}
\max_{X_i, Y_i} & \quad X_i^\alpha Y_i^{1 - \alpha} \\
\text{subject to} & \quad P_i X_i + Y_i \leq w_i L \\
& \quad X_i = \left( n x_{ii}^{\frac{\sigma - 1}{\sigma}} + n x_{ij}^{\frac{\sigma - 1}{\sigma}} \right)^{\frac{\sigma}{\sigma - 1}}
\end{split}
\end{equation}

**Production**

- $n$ firms producing differentiated goods and outside (agricultural) sector

\begin{equation} \label{eq:Pi}
\begin{split}
\max_{p_i} & \quad \Pi_i(p_i) = \left( p_i - w_i \right) \left( x_{ii}^\star(p_i) + x_{ji}^\star(p_i) \right) \\
\text{subject to} & \quad x_{ii}^\star(p_i) = p_i^{-\sigma} P_i^{\sigma - 1} \alpha w_i L \\
& \quad x_{ji}^\star(p_i) = (\tau_j p_i)^{-\sigma} P_j^{\sigma - 1} \alpha w_j L
\end{split}
\end{equation}

**Revenue**

\begin{equation} \label{eq:revenue}
r_i(\tau_i) = n (\tau_i - 1) p_j x_{ij}^\star(\tau_i p_j)
\end{equation}

<a href="#/dpe" style="float: right;">Back</a>

## Government Preferences {id="Gprefs"}

**Lemma `r qccv`:** `r LqccvText`

<hr style="height:1em; visibility:hidden;" />

<center><hr width="50%"></center>

<hr style="height:1em; visibility:hidden;" />

**Lemma `r tauj`:** `r LtaujText`

<a href="#/iso" style="float: right;">Back</a>

## Noncooperative Equilibrium {id="nceDef"}

**Best Responses Functions**

$$
\tau_i(a_i, \tau_j) = \text{argmax}_{\tau_i \in [1, \overline{\tau}]} G_i(\tau_i, \tau_j; a_i)
$$
and
$$
\tau_j(a_j, \tau_i) = \text{argmax}_{\tau_j \in [1, \overline{\tau}]} G_j(\tau_i, \tau_j; a_j)
$$

<hr style="height:1em; visibility:hidden;" />

<center><hr width="50%"></center>

<hr style="height:1em; visibility:hidden;" />

**Definition `r nceq`:** `r DnceqText`

<hr style="height:1em; visibility:hidden;" />

<center><hr width="50%"></center>

<hr style="height:1em; visibility:hidden;" />

**Lemma `r taui`:** `r LtauiText`

<a href="#/nce" style="float: right;">Back</a>

## Bargaining {id="bargaining"}

**Successful Regime Change**

<hr style="height:1em; visibility:hidden;" />
\begin{equation} \label{eq:Gbar}
\overline{G}_i(a_i) = G_i(\tau_i^\star(a_i), \tau_j^\star(a^\star) | a_i ) = G_i(\tau_i^\star(a_i), 1 | a_i)
\end{equation}
<hr style="height:1em; visibility:hidden;" />

**Foreign Imposition of Regime Change**

<hr style="height:1em; visibility:hidden;" />
\begin{equation} \label{eq:Gubar}
\underline{G}_i(a_i, a_j) = G_i(\tau_i^\star(a^\star), \tau_j^\star(a_j) | a_i) = G_i(1, \tau_j^\star(a_j) | a_i)
\end{equation}
<hr style="height:1em; visibility:hidden;" />

**Foreign Government's Expected Utility for War**

<hr style="height:1em; visibility:hidden;" />
$$
\widehat{G}_j(a_j, a_i) = (1 - \rho) \overline{G}_j(a_j) + \rho \underline{G}_j(a_j, a_i) - c_j
$$
<hr style="height:1em; visibility:hidden;" />

<a href="#/barEnv" style="float: right;">Back</a>

## The Commercial-Democratic Peace {id="comDemPeace"}

```{r emp_wars, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE, fig.align="center", fig.height=6}

source("figs/emp_wars.R")

polityDensity <- polityDensity + theme(plot.title = element_blank())

polityDensity + empty + main + tradeIntDensity + polityRail + empty + plot_layout(ncol=2, widths=c(8,1), heights=c(1,15,2))

```

<a href="#/implications" style="float: right;">Back</a>

<hr style="height:5em; visibility:hidden;" />
