---
title: "Gunboat Diplomacy"
subtitle: "Political Bias, Trade Policy, and War"
author: Brendan Cooley
date: "19 January 2019"
output: 
  revealjs::revealjs_presentation:
    template: "cooley-reveal.html"
    css: "css/cooley-reveal.css"
    transition: none
    self_contained: true
    # reveal_plugins: ["notes"]
    lib_dir: index_files
    reveal_options:
      slideNumber: true
    includes:
      after_body: plugins.html
---

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
# TODO: vertical slides currently not behaving

if (file.exists('references.RData')) load('references.RData')

# get helper functions
source('figs/source.R')

# get params
source('figs/params.R')

```

## The Modern Economic Peace, 1870-2014

```{r emp_wars, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE, fig.align="center", fig.height=6}

source("figs/emp_wars.R")

polityDensity <- polityDensity + theme(plot.title = element_blank())

polityDensity + empty + main + tradeIntDensity + polityRail + empty + plot_layout(ncol=2, widths=c(8,1), heights=c(1,15,2))

```

## Why?

. . . 

**Dominant Paradigm:** Trade mediates *preexisting* conflicts of interest

- Governments value trade, conflict disrupts trade
  - $\implies$ Commercial peace hypothesis: economic integration reduces war
- Conflicts of interest: territorial, ideological, etc

. . . 

**Commercial Policy Objectives**

- Governments weakly mercantilistic, desiring
  - Some degree of trade protection at home
  - Trade liberalization or *market access* abroad

. . . 

**Market Access Externalities**

- Protectionist barriers *shift profits* from foreign to home firms
- Thus, trade policy itself generates conflicts of interest between mercantilist governments

<aside class="notes">
- Govs often willing to risk war to pursue commercial policy objectives, see Perry Expeditions, Opium Wars
</aside>

## Political Bias

**Local definition:** Degree to which government internalizes *narrow* (protectionist) interests of firms at the expense of *broad* (liberal) interests of consumers

- Grossman and Helpman (1994), Bueno de Mesquita et al (2004)

. . . 

**Regimes and Political Bias**

- Democracies afford consumers access to policymaking process, more liberal trade policy preferences than autocracies (Milner and Kubota 2005)

. . . 

**Argument in Brief:** For democracies, liberal preferences $\implies$ smaller conflicts of interest $\implies$ fewer wars

- Additionally, liberal preferences $\implies$ more trade
- Spurious correlation between trade and peace

## Model Structure {id="modelStructure"}

**Bargaining Environment**

- Two governments bargain over trade policies, $\widetilde{\boldsymbol{\tau}} = \left\{ \tau_i, \tau_j \right\}$
- "Home" gov $i$ makes TIOLI offer to "foreign" gov $j$
- Information about $j$'s costs of war held privately

<hr style="height:5px; visibility:hidden;" />

$$
\widetilde{\boldsymbol{\tau}}^\star(a_i) = \text{argmax } \widetilde{G}_i \left( \widetilde{\boldsymbol{\tau}}(a_i), \omega^\star(\widetilde{\boldsymbol{\tau}}(a_i) | a_j) | a_i \right)
$$
<hr style="height:5px; visibility:hidden;" />

- Foreign can accept or declare war
<hr style="height:5px; visibility:hidden;" />
$$
\omega^\star(\widetilde{\boldsymbol{\tau}} | a_j) = \text{argmax } \widetilde{G}_j \left( \widetilde{\boldsymbol{\tau}}, \omega(\widetilde{\boldsymbol{\tau}} | a_j ) \right)
$$
<hr style="height:5px; visibility:hidden;" />

<a href="#/bargaining" style="float: right;">Bargaining</a>

. . . 

**International Economy**

- Representative consumer and $n$ firms in each economy, monopolistic competition

    - Krugman 1980, Venables 1987, Ossa 2012
  
<a href="#/economy" style="float: right;">Economy</a>

## Government Preferences I {id="GpreferencesI"}

<hr style="height:5px; visibility:hidden;" />

\begin{equation} \label{eq:G}
G_i(\tau_i, \tau_j | a_i) = a_i V_i^x(\tau_i) + \Pi_i(\tau_i, \tau_j) + r_i(\tau_i)
\end{equation}

<hr style="height:5px; visibility:hidden;" />

- $V_i^x(\tau_i)$ - consumer welfare
- $\Pi_i(\tau_i, \tau_j)$ - firm profits
- $r_i(\tau_i)$ - tariff revenue

*$a_i$ is measure of sensitivity to interests of consumers*

<a href="#/assumptions" style="float: right;">Assumptions</a>

## Government Preferences II {id="GpreferencesII"}

```{r G, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, dpi=300, cache=TRUE}

source("figs/G.R")

GPlot

```

## Non-cooperative Equilibrium {id="nce"}

```{r iso, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, dpi=300, cache=TRUE}

source("figs/iso.R")

isoPlot

```

<aside class="notes">
- Discuss where each ideal point is.
- Changing bias parameter shifts best response curve around
- Govs are perfectly open when bias is lowest
</aside>

<a href="#/nceDef" style="float: right;">Definition</a>

## Non-cooperative Equilibrium

```{r br, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, dpi=300, cache=TRUE}

brPlot

```

<a href="#/nceDef" style="float: right;">Definition</a>

## Regime Change and Conflicts of Interest

**Optimal Puppet Regimes**

- When a government wins a war, it earns the right to replace the vanquished government with a "puppet" that prefers lower barriers to trade

<hr style="height:5px; visibility:hidden;" />
$$
\max_{a \in (0, \bar{a}]} G_i( \tau_i^\star(a_i), \tau_j^\star(a) | a_i )
$$
<hr style="height:5px; visibility:hidden;" />

- Losing governments have puppet's policies imposed on them

. . . 

**Conflicts of Interest**

- Utility difference between (costlessly) winning a war for regime change and being replaced by a puppet

<hr style="height:5px; visibility:hidden;" />

\begin{equation} \label{eq:Gamma}
\Gamma_i(a_i, a_j) = \overline{G}_i(a_i) - \underline{G}_i(a_i, a_j)
\end{equation}

## Bargaining Environment

```{r bar, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, dpi=300}

source("figs/bar.R")

barPlot

```

<aside class="notes">
- No conflict of interest for maximally liberal governments
</aside>

## Results

<hr style="height:4em; visibility:hidden;" />

**Proposition `r Pgamma`:** Conflicts of interest smaller for low bias (democratic) governments.

. . . 

**Proposition `r Pwar`:** The probability of war is lower for low bias (democratic) governments.

. . . 

**Proposition `r PeqTrade`:** Equilibrium trade flows are higher for low bias (democratic) governments.

. . . 

<aside class="notes">
- Risk-reward dilemma more stark for high bias (autocratic) governments
</aside>

## Conclusion

- Equilibrium trade policies balance
  - Domestic political interests
  - Foreign military constraints
  
. . . 

- *Threat* of regime change sufficient to produce changes in policies
  - Shadow of military power in international political economy

## Thank You {.center}

[brendancooley.com](brendancooley.com)

[bcooley@princeton.edu](bcooley@princeton.edu)

<small>**Title Slide Image Credit:** Charles Severin (American lithographer, born between 1808-1820; died ca. 1860). 1853 (creation). The American Expedition, The American Expedition, Under Commodore Perry, Landing in Japan, July 14, 1853, Overall view. visual works; prints (visual works); planographic prints; lithographs. https://library.artstor.org/asset/SS35100_35100_35234600</small>

## Assumptions {id="assumptions"}

<a href="#/GpreferencesI" style="float: right;">Back</a>

## Non-cooperative Equilibrium {id="nceDef"}

<a href="#/nce" style="float: right;">Back</a>

## Bargaining {id="bargaining"}

<a href="#/modelStructure" style="float: right;">Back</a>

## International Economy {id="economy"}

<a href="#/modelStructure" style="float: right;">Back</a>