---
title: "Gunboat Diplomacy"
subtitle: "Political Bias, Trade Policy, and War"
author: Brendan Cooley
date: "19 January 2019"
output: 
  revealjs::revealjs_presentation:
    template: "cooley-reveal.html"
    css: "css/cooley-reveal.css"
    transition: none
    self_contained: true
    # reveal_plugins: ["notes"]
    lib_dir: index_files
    reveal_options:
      slideNumber: true
    includes:
      after_body: plugins.html
---

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
# TODO: vertical slides currently not behaving
# TODO: speaker notes don't work with incremental reveal
# TODO: nested bulleted lists disappear after compilation, fine when knitting


if (file.exists('references.RData')) load('references.RData')

# get helper functions
source('figs/source.R')

# get params
source('figs/params.R')

```

## The Modern Economic Peace, 1870-2014 (Coe)

```{r emp_wars, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE, fig.align="center", fig.height=6}

source("figs/emp_wars.R")

polityDensity <- polityDensity + theme(plot.title = element_blank())

polityDensity + empty + main + tradeIntDensity + polityRail + empty + plot_layout(ncol=2, widths=c(8,1), heights=c(1,15,2))

```

## Why?

. . . 

**Dominant Paradigm:** Trade mediates *preexisting* conflicts of interest

- Governments value trade, conflict disrupts trade
    - $\implies$ Commercial peace hypothesis
- Conflicts of interest: territorial, ideological, etc

. . . 

**Commercial Policy Objectives**

- Governments weakly mercantilistic, desiring
    - Some degree of trade protection at home
    - Trade liberalization or *market access* abroad

. . . 

**Market Access Externalities**

- Protectionist barriers *shift profits* from foreign to home firms
- Thus, trade policy itself generates conflicts of interest between mercantilist governments

. . . 

<p class="center">*Perry Expedition: Governments willing to threaten war to open foreign markets*</p>

<aside class="notes">
- Govs often willing to risk war to pursue commercial policy objectives, see Perry Expeditions, Opium Wars
</aside>

## Political Bias (Jackson and Morelli 2007)

**Local definition:** Degree to which government internalizes *narrow* (protectionist) interests of firms at the expense of *broad* (liberal) interests of consumers

- Grossman and Helpman (1994), Bueno de Mesquita et al (2004)

. . . 

**Regimes and Political Bias**

- Democracies afford consumers (voters) access to policymaking process, more liberal trade policy preferences than autocracies (Mayer 1984, Grossman and Helpman 1996, Milner and Kubota 2005)

. . . 

**Argument in Brief:** For democracies, liberal preferences $\implies$ smaller market access externalities $\implies$ smaller conflicts of interest $\implies$ fewer wars

- Additionally, liberal preferences $\implies$ more trade
- Spurious correlation between trade and peace

## Model Structure {id="modelStructure"}

**Bargaining Environment**

- Two governments bargain over trade policies, $\widetilde{\boldsymbol{\tau}} = \left\{ \tau_i, \tau_j \right\}$
- "Home" gov $i$ makes TIOLI offer to "foreign" gov $j$
- Information about $j$'s costs of war held privately

<hr style="height:5px; visibility:hidden;" />

$$
\widetilde{\boldsymbol{\tau}}^\star(a_i) = \text{argmax } \widetilde{G}_i \left( \widetilde{\boldsymbol{\tau}}(a_i), \omega^\star(\widetilde{\boldsymbol{\tau}}(a_i) | a_j) | a_i \right)
$$
<hr style="height:5px; visibility:hidden;" />

- Foreign can accept or declare war
<hr style="height:5px; visibility:hidden;" />
$$
\omega : \widetilde{\boldsymbol{\tau}}(a_i) \rightarrow \left\{ \text{war}, \neg \text{war} \right\}
$$

<a href="#/bargaining" style="float: right;">Bargaining</a>

. . . 

**International Economy**

- Representative consumer and $n$ firms in each economy, monopolistic competition
    - Krugman 1980, Venables 1987, Ossa 2012
  
<a href="#/economy" style="float: right;">Economy</a>

## Government Preferences I {id="GpreferencesI"}

<hr style="height:5px; visibility:hidden;" />

\begin{equation} \label{eq:G}
G_i(\tau_i, \tau_j | a_i) = a_i V_i^x(\tau_i) + \Pi_i(\tau_i, \tau_j) + r_i(\tau_i)
\end{equation}

<hr style="height:5px; visibility:hidden;" />

- $V_i^x(\tau_i)$ - consumer welfare
    - decreasing in $\tau_i$
- $\Pi_i(\tau_i, \tau_j)$ - firm profits
    - increasing in $\tau_i$, decreasing in $\tau_j$
- $r_i(\tau_i)$ - tariff revenue
    - non-monotonic in $\tau_i$

<p class="center">*$a_i$ is measure of government's sensitivity to interests of consumers*</p>

<a href="#/assumptions" style="float: right;">Assumptions</a>

## Government Preferences II {id="GpreferencesII"}

```{r G, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5.5, dpi=300, cache=TRUE}

source("figs/G.R")

GPlot

```

## Non-cooperative Equilibrium {id="nce"}

```{r iso, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, dpi=300, cache=TRUE}

source("figs/iso.R")

isoPlot

```

<aside class="notes">
- Discuss where each ideal point is.
- Changing bias parameter shifts best response curve around
- Govs are perfectly open when bias is lowest
</aside>

<a href="#/nceDef" style="float: right;">Definition</a>

## Non-cooperative Equilibrium

```{r br, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, dpi=300, cache=TRUE}

brPlot

```

<a href="#/nceDef" style="float: right;">Definition</a>

## Regime Change and Conflicts of Interest

**Optimal Puppet Regimes**

- When a government wins a war, it earns the right to replace the vanquished government with a "puppet" that prefers lower barriers to trade

<hr style="height:5px; visibility:hidden;" />
$$
\max_{a \in (0, \overline{a}]} G_i( \tau_i^\star(a_i), \tau_j^\star(a) | a_i )
$$
<hr style="height:5px; visibility:hidden;" />

- Losing governments have puppet's policies imposed on them

. . . 

**Conflicts of Interest**

- Utility difference between (costlessly) winning a war for regime change and being replaced by a puppet

<hr style="height:5px; visibility:hidden;" />

\begin{equation} \label{eq:Gamma}
\Gamma_i(a_i, a_j) = \overline{G}_i(a_i) - \underline{G}_i(a_i, a_j)
\end{equation}

## Bargaining Environment

```{r bar, echo=FALSE, warning=FALSE, message=FALSE, fig.height=5, dpi=300}

source("figs/bar.R")

barPlot

```

<aside class="notes">
- No conflict of interest for maximally liberal governments
</aside>

## Results

<hr style="height:4em; visibility:hidden;" />

**Proposition `r Pgamma`:** Conflicts of interest smaller for low bias (democratic) governments.

. . . 

**Proposition `r Pwar`:** The probability of war is lower for low bias (democratic) governments.

. . . 

**Proposition `r PeqTrade`:** Equilibrium trade flows are higher for low bias (democratic) governments.

. . . 

<p class="center">*The Modern Economic Peace*</p>

<aside class="notes">
- Risk-reward dilemma more stark for high bias (autocratic) governments
</aside>

## Conclusion

**Trade Policy in the Shadow of Power**

- Equilibrium trade policies balance
    - Domestic political interests
    - Foreign military constraints
  
. . . 

- *Threat* of regime change sufficient to produce changes in policies

. . . 

- Exists no simple mapping between domestic preferences and trade policy outcomes (Gawande et al 2009)
    - IR parlance: "second image" and "second image reversed"
  
. . . 

**Conflicts of Interest versus Bargaining Failures**

- Fearon 1995: *given* a conflict of interest, what prevents peaceful settlement?
- Moravcsik 1997: what do governments want? and why do their objectives bring them into conflict with one another?


## Thank You {.center}

[brendancooley.com](brendancooley.com)

[bcooley@princeton.edu](bcooley@princeton.edu)

<small>**Title Slide Image Credit:** Charles Severin (American lithographer, born between 1808-1820; died ca. 1860). 1853 (creation). The American Expedition, Under Commodore Perry, Landing in Japan, July 14, 1853, Overall view. visual works; prints (visual works); planographic prints; lithographs. https://library.artstor.org/asset/SS35100_35100_35234600</small>

## Bargaining {id="bargaining"}

- $c_i$ - home government's costs of war
- $c_j \sim F$ - home's belief about foreign's costs of war

    - $F$ uniform on $[0, \overline{c}]$
  
- $\rho$ - probability home government wins war

**Successful Regime Change**

<hr style="height:5px; visibility:hidden;" />
\begin{equation} \label{eq:Gbar}
\overline{G}_i(a_i) = G_i(\tau_i^\star(a_i), \tau_j^\star(a^\star) | a_i ) = G_i(\tau_i^\star(a_i), 1 | a_i)
\end{equation}
<hr style="height:5px; visibility:hidden;" />

**Foreign Imposition of Regime Change**

<hr style="height:5px; visibility:hidden;" />
\begin{equation} \label{eq:Gubar}
\underline{G}_i(a_i, a_j) = G_i(\tau_i^\star(a^\star), \tau_j^\star(a_j) | a_i) = G_i(1, \tau_j^\star(a_j) | a_i)
\end{equation}
<hr style="height:5px; visibility:hidden;" />

**Foreign Government's Expected Utility for War**

<hr style="height:5px; visibility:hidden;" />
$$
\widehat{G}_j(a_j, a_i) = (1 - \rho) \overline{G}_j(a_j) + \rho \underline{G}_j(a_j, a_i) - c_j
$$
<hr style="height:5px; visibility:hidden;" />

<a href="#/modelStructure" style="float: right;">Back</a>

## International Economy I {id="economy"}

**Consumers**

<hr style="height:5px; visibility:hidden;" />
\begin{equation} \label{eq:cMax}
\begin{split}
\max_{X_i, Y_i} & \quad X_i^\alpha Y_i^{1 - \alpha} \\
\text{subject to} & \quad P_i X_i + Y_i \leq w_i L
\end{split}
\end{equation}
<hr style="height:5px; visibility:hidden;" />

- $X_i$ CES aggregate of differentiated manufactured goods

**Firms**

- $n$ firms producing manufactured goods in each economy

<hr style="height:5px; visibility:hidden;" />
\begin{equation} \label{eq:Pi}
\begin{split}
\max_{p_i} & \quad \Pi_i(p_i) = \left( p_i - w_i \right) \left( x_{ii}^\star(p_i) + x_{ji}^\star(p_i) \right) \\
\text{subject to} & \quad x_{ii}^\star(p_i) = p_i^{-\sigma} P_i^{\sigma - 1} \alpha w_i L \\
& \quad x_{ji}^\star(p_i) = (\tau_j p_i)^{-\sigma} P_j^{\sigma - 1} \alpha w_j L
\end{split}
\end{equation}
<hr style="height:5px; visibility:hidden;" />

## International Economy II

*Economic equilibrium* is pair of wages $\left\{ w_i, w_j \right\}$ such that international goods market and local factor markets clear

<a href="#/modelStructure" style="float: right;">Back</a>

## Assumptions {id="assumptions"}

<hr style="height:2em; visibility:hidden;" />

**Assumption `r Akappa`:** (costs of war are bounded) $c_i < \kappa$ where $\kappa$ is a postive constant defined in the Appendix.

**Assumption `r aAlpha`:** (agricultural sector sufficiently large)
<hr style="height:5px; visibility:hidden;" />
$$
\alpha < \frac{2}{3} \frac{\sigma}{\sigma - 1}
$$ 
<hr style="height:5px; visibility:hidden;" />

**Assumption `r aA`:** (governments are weak mercantilists) $a_i \in (0, \overline{a})$ with
<hr style="height:5px; visibility:hidden;" />
$$
\overline{a} = (2n)^{\frac{1}{1-\sigma}} \left( \frac{\sigma}{\sigma - 1} + \frac{1}{2} \right)
$$
<hr style="height:5px; visibility:hidden;" />

<a href="#/GpreferencesI" style="float: right;">Back</a>

## Non-cooperative Equilibrium {id="nceDef"}

<hr style="height:3em; visibility:hidden;" />

**Definition `r nceq`:** A *noncooperative equilibrium* is a pair of policies $\left\{ \tau_i^\star(a_i), \tau_j^\star(a_j) \right\}$ such that 
<hr style="height:5px; visibility:hidden;" />
$$
\tau_i^\star(a_i) = \text{argmax } G_i(\tau_i | \tau_j^\star(a_j), a_i)
$$
<hr style="height:5px; visibility:hidden;" />
and
<hr style="height:5px; visibility:hidden;" />
$$
\tau_j^\star(a_j) = \text{argmax } G_j(\tau_j | \tau_i^\star(a_i), a_j)
$$
<hr style="height:5px; visibility:hidden;" />


**Lemma `r taui`:** $\tau_i^\star(a_i)$ is decreasing in $a_i \in (0, \overline{a})$ with $\tau_i^\star(\overline{a}) = 1$.

<a href="#/nce" style="float: right;">Back</a>