```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
PeeqProof <- knit_child("../proofs/Peeq.md")
```

**Proposition `r eeqP`:** `r PeeqProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
LqccvProof <- knit_child("../proofs/Lqccv.rmd")
```

**Lemma `r Lqccv`:** `r LqccvProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
LtaujProof <- knit_child("../proofs/Ltauj.md")
```

**Lemma `r tauj`:** `r LtaujProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
LtauiProof <- knit_child("../proofs/Ltaui.md")
```

**Lemma `r taui`:** `r LtauiProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
PastarProof <- knit_child("../proofs/Pastar.md")
```

**Proposition `r astar`:** `r PastarProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
PgammaProof <- knit_child("../proofs/Pgamma.md")
```

**Proposition `r Pgamma`:** `r PgammaProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
LtauCornerProof <- knit_child("../proofs/LtauCorner.md")
```

**Lemma `r LtauCorner`:** `r LtauCornerProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
LaEpsilonProof <- knit_child("../proofs/LaEpsilon.rmd")
```

**Lemma `r LaEpsilon`:** `r LaEpsilonProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
PwarProof <- knit_child("../proofs/Pwar.rmd")
```

**Proposition `r Pwar`:** `r PwarProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
LparetoProof <- knit_child("../proofs/Lpareto.md")
```

**Lemma `r Lpareto`:** `r LparetoProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
LtildeTauProof <- knit_child("../proofs/LtildeTau.md")
```

**Lemma `r LtildeTau`:** `r LtildeTauProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
PeqTauProof <- knit_child("../proofs/PeqTau.md")
```

**Proposition `r PeqTau`:** `r PeqTauProof` 

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
PeqTradeProof <- knit_child("../proofs/PeqTrade.md")
```

**Proposition `r PeqTrade`:** `r PeqTradeProof` 

