Restatements of results from the main text proceed all proofs. Lemmas `r Ltauj`, and `r Ltaui` exploit the following definitions:
$$
A(\tau_i) = p^\star x_{ij}^\star(\tau_i) (\alpha I(\tau_i))^{-1} = \left( 1 + \tau_i^{1-\sigma} \right)^{-1} \tau_i^{-\sigma}
$$
$$
B(\tau_i) = (\sigma - 1) A(\tau_i) - \sigma \tau_i^{-1} .
$$


```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
PeeqProof <- knit_child("../proofs/Peeq.md")
```

**Proposition `r Peeq`:** `r PeeqText`

**Proof:** `r PeeqProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
LintProof <- knit_child("../proofs/Lint.md")
```

**Lemma `r Lint`:** `r LintText`

**Proof:** `r LintProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
LtaujProof <- knit_child("../proofs/Ltauj.md")
```

**Lemma `r Ltauj`:** `r LtaujText`

**Proof:** `r LtaujProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
LtauiProof <- knit_child("../proofs/Ltaui.md")
```

**Lemma `r Ltaui`:** `r LtauiText`

**Proof:** `r LtauiProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
PastarProof <- knit_child("../proofs/Pastar.md")
```

**Proposition `r Pastar`:** `r PastarText`

**Proof:** `r PastarProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
PgammaProof <- knit_child("../proofs/Pgamma.md")
```

**Proposition `r Pgamma`:** `r PgammaText`

**Proof: **`r PgammaProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
LtauCornerProof <- knit_child("../proofs/LtauCorner.md")
```

**Lemma `r LtauCorner`:** `r LtauCornerText`

**Proof:** `r LtauCornerProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
LaEpsilonProof <- knit_child("../proofs/LaEpsilon.rmd")
```

**Lemma `r LaEpsilon`:** `r LaEpsilonText`

**Proof:** `r LaEpsilonProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
PwarProof <- knit_child("../proofs/Pwar.rmd")
```

**Proposition `r Pwar`:** `r PwarText`

**Proof:** `r PwarProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
LparetoProof <- knit_child("../proofs/Lpareto.md")
```

**Lemma `r Lpareto`:** `r LparetoText`

**Proof:** `r LparetoProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
LtildeTauProof <- knit_child("../proofs/LtildeTau.md")
```

**Lemma `r LtildeTau`:** `r LtildeTauText`

**Proof:** `r LtildeTauProof`

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
PeqTauProof <- knit_child("../proofs/PeqTau.md")
```

**Proposition `r PeqTau`:** `r PeqTauText`

**Proof:** `r PeqTauProof` 

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
PeqTradeProof <- knit_child("../proofs/PeqTrade.rmd")
```

**Proposition `r PeqTrade`:** `r PeqTradeText`

**Proof:** `r PeqTradeProof` 

