The result follows from a series of Lemmas.

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
qccv_tick <- 1
qccv_rev <- qccv_tick
```

**Preliminaries:** Let
$$
A(\tau_i) = \left( 1 + \tau_i^{1-\sigma} \right)^{-1} \tau_i^{-\sigma}
$$
$$
B(\tau_i) = (\sigma - 1) A(\tau_i) - \sigma \tau_i^{-1}
$$
$$
C(\tau_i) = (\tau_i - 1) B(\tau_i) + 1
$$
and
$$
\lambda(\tau_i) = \frac{r_i(\tau_i)}{I_i(\tau_i)}
$$
with
$$
A^\prime(\tau_i) = A(\tau_i) B(\tau_i)
$$
and
$$
B^\prime(\tau_i) = (\sigma - 1) A(\tau_i) B(\tau_i) + \sigma \tau_i^{-2}
$$

**Lemma `r Lqccv`.`r qccv_rev`:** $r_i^\prime(\tau_i) > 0 \implies r_i^{\prime \prime}(\tau_i) < 0$

**Proof:** Using the above quantities, we can write
$$
x_{ij}^{\star \prime}(\tau_i) = B(\tau_i) x_{ij}^\star(\tau_i) + \frac{x_{ij}^\star(\tau_i)}{I_i(\tau_i)} r_i^\prime(\tau_i)
$$
and 
\begin{align*}
r_i^\prime(\tau_i) &= (\tau_i - 1) p^\star x_{ij}^{\star \prime}(\tau_i) + p^\star x_{ij}^\star(\tau_i) \\
r_i^\prime(\tau_i) &= B(\tau_i) r_i(\tau_i) + \lambda(\tau_i) r_i^\prime(\tau_i) + p^\star x_{ij}^\star(\tau_i) \\
(1 - \lambda(\tau_i)) r_i^\prime(\tau_i) &= B(\tau_i) r_i(\tau_i) + p^\star x_{ij}^\star(\tau_i) \\
(\tau_i - 1) (1 - \lambda(\tau_i)) r_i^\prime(\tau_i) &= (\tau_i - 1) B(\tau_i) r_i(\tau_i) + r_i(\tau_i) \\
(\tau_i - 1) (1 - \lambda(\tau_i)) r_i^\prime(\tau_i) &= r_i(\tau_i) \left( (\tau_i - 1) B(\tau_i) + 1 \right) \\
(\tau_i - 1) (1 - \lambda(\tau_i)) r_i^\prime(\tau_i) &= r_i(\tau_i) C(\tau_i)
\end{align*}

Note that because $\lambda(\tau_i) < 1$ and $B(\tau_i) < 0$, then $C(\tau_i) \in (0, 1)$ whenever $r_i^\prime(\tau_i) > 0$. Also, the definition of $r_i(\tau_i)$ implies
$$
\tau_i - 1 = \frac{r_i(\tau_i)}{p^\star x_{ij}^\star(\tau_i)}
$$

Taking the second derivative, we have
\begin{align*}
(\tau_i - 1) (1 - \lambda(\tau_i)) r_i^{\prime \prime}(\tau_i) =& - \left( (1 - \lambda(\tau_i)) r_i^\prime(\tau_i) - (\tau_i - 1) \lambda^\prime(\tau_i) r_i^\prime(\tau_i) \right) + C(\tau_i) r_i^\prime(\tau_i) + C^\prime(\tau_i) r_i(\tau_i) \\
=& - \left( (1 - \lambda(\tau_i)) r_i^\prime(\tau_i) - (\tau_i - 1) (1 - \lambda(\tau_i)) r_i^\prime(\tau_i)^2 I_i(\tau_i)^{-1} \right) + C(\tau_i) r_i^\prime(\tau_i) + C^\prime(\tau_i) r_i(\tau_i) \\
=& - (1 - \lambda(\tau_i)) r_i^\prime(\tau_i) \left( 1 - (\tau_i - 1) I_i(\tau_i)^{-1} r_i^\prime(\tau_i) \right) + C(\tau_i) r_i^\prime(\tau_i) + C^\prime(\tau_i) r_i(\tau_i) \\
=& - (1 - \lambda(\tau_i)) r_i^\prime(\tau_i) \left( 1 - \lambda(\tau_i) \frac{r_i^\prime(\tau_i)}{p^\star x_{ij}^\star(\tau_i)} \right) + C(\tau_i) r_i^\prime(\tau_i) + C^\prime(\tau_i) r_i(\tau_i) \\
=& - (1 - \lambda(\tau_i)) r_i^\prime(\tau_i) \left( 1 - \lambda(\tau_i) \frac{C(\tau_i)}{(1 - \lambda(\tau_i))} \right) + C(\tau_i) r_i^\prime(\tau_i) + C^\prime(\tau_i) r_i(\tau_i) \\
=& - r_i^\prime(\tau_i) \left( 1 - (1 - C(\tau_i)) \lambda(\tau_i) \right) + C(\tau_i) r_i^\prime(\tau_i) + C^\prime(\tau_i) r_i(\tau_i) \\
=& \underbrace{- r_i^\prime(\tau_i) \left( 1 - (1 - C(\tau_i)) \lambda(\tau_i) \right) + C(\tau_i) r_i^\prime(\tau_i)}_{<0 \text{ (I)}} + \underbrace{C^\prime(\tau_i) r_i(\tau_i)}_{<0 \text{ (II)}}
\end{align*}

Inequality (I) holds because $\lambda(\tau_i) < 1$. To see why (II) holds, note
\begin{align*}
\tau_i C^\prime(\tau_i) &= \tau_i (\tau_i - 1) B^\prime(\tau_i) + \tau_i B(\tau_i) \\
&= (\tau_i - 1) \tau_i \left( (\sigma - 1) A(\tau_i) B(\tau_i) + \sigma \tau_i^{-2} \right) + \tau_i \left( (\sigma - 1) A(\tau_i) - \sigma \tau_i^{-1} \right) \\
&= (\sigma - 1) \tau_i A(\tau_i) \tau_i B(\tau_i) + \sigma - \tau_i B^\prime(\tau_i) + (\sigma - 1) \tau_i A(\tau_i) - \sigma \\
&= (\sigma - 1) \tau_i A(\tau_i) \underbrace{\left( \tau_i B(\tau_i) + 1 \right)}_{<0} - \tau_i B^\prime(\tau_i)
\end{align*}
where the inequality follows from the fact that $\tau_i B(\tau_i) < -1$. $\blacksquare$

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
qccv_tick <- qccv_tick + 1
qccv_rprime <- qccv_tick
```

**Lemma `r Lqccv`.`r qccv_rprime`:** $G_i^\prime(\tau_i; a_i) = 0 \implies r_i^{\prime}(\tau_i) > 0$ for all $a_i > \ubar{a}_i$

**Proof:** The first order condition is
\begin{equation} \label{eq:Gfoc}
0 = - \alpha a_i V_i(\tau_i) A(\tau_i) + a_i r_i^\prime(\tau_i) P_i(\tau_i)^{-\alpha} + \Pi_i^\prime(\tau_i)
\end{equation}.
Rearranging,
\begin{align*}
\alpha a_i V_i(\tau_i) A(\tau_i) - \Pi_i^\prime(\tau_i) &= a_i r_i^\prime(\tau_i) P_i(\tau_i)^{-\alpha} \\
\underbrace{ \frac{P_i(\tau_i)^\alpha}{a_i} \left( \alpha a_i V_i(\tau_i) A(\tau_i) - \Pi_i^\prime(\tau_i) \right)}_{>0} &= r_i^\prime(\tau_i)
\end{align*}
By construction, the left hand side is zero when $a_i = \ubar{a}$. It is therefore strictly positive for all $a_i > \ubar{a}$. $\blacksquare$

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
qccv_tick <- qccv_tick + 1
qccv_bound <- qccv_tick
```

**Lemma `r Lqccv`.`r qccv_bound`:** $G_i^{\prime}(\tau_i; \ubar{a}) = 0$ and $G_i^{\prime}(\tau_i; a_i) = 0 \implies G_i^{\prime \prime}(\tau_i; \ubar{a}) > G_i^{\prime \prime}(\tau_i; a_i)$ for all $a_i > \ubar{a}$.

**Proof:** Note first that when $G_i^{\prime}(\tau_i; a_i)$, $V_i^{\prime \prime}(\tau_i) < 0$ for all $a_i > \ubar{a}$. 
\begin{align*}
k(\alpha)^{-1} V_i^{\prime \prime}(\tau_i) &= P_i(\tau_i)^{-\alpha} r_i^{\prime \prime} (\tau_i) - \alpha A(\tau_i) \left( V_i^\prime(\tau_i) + V_i(\tau_i) B(\tau_i) + r_i^\prime(\tau_i) P_i(\tau_i)^{-\alpha} \right) \\
&= P_i(\tau_i)^{-\alpha} r_i^{\prime \prime} (\tau_i) - \alpha A(\tau_i) \left( 2 r_i^\prime(\tau_i) P_i(\tau_i)^{-\alpha} - \alpha V_i(\tau_i) A(\tau_i) + V_i(\tau_i) B(\tau_i) \right)
\end{align*}
When $G_i^{\prime}(\tau_i; a_i) = 0$, $P_i(\tau_i)^{-\alpha} r_i^\prime(\tau_i) = \alpha V_i(\tau_i) A_i(\tau_i) - \frac{1}{a_i} \Pi_i^\prime(\tau_i)$. Then, 
$$
k(\alpha)^{-1} V_i^{\prime \prime}(\tau_i) = P_i(\tau_i)^{-\alpha} r_i^{\prime \prime} (\tau_i) - \alpha A(\tau_i) \underbrace{\left( \alpha V_i(\tau_i) A(\tau_i) - \frac{2}{a_i} \Pi_i^\prime(\tau_i) + V_i(\tau_i) B(\tau_i) \right)}_{\phi(\tau_i)}
$$
Because $B(\tau_i) < 0$, $\phi_i(\tau_i) < 0$ when $a_i = \ubar{a}$. As $a_i \rightarrow \infty$, 
\begin{align*}
\phi(\tau_i) \rightarrow & \alpha V_i(\tau_i) A(\tau_i) + V_i(\tau_i) B(\tau_i) \\
=& \alpha V_i(\tau_i) A(\tau_i) + V_i(\tau_i) \left( (\sigma - 1) A(\tau_i) - \sigma \tau_i^{-1} \right) \\
<& V_i(\tau_i) \left( \sigma A(\tau_i) - \sigma \tau_i^{-1} \right) < 0
\end{align*}
So $\phi_i(\tau_i) < 0$ whenever $a_i \in (\ubar{a}, \infty)$. Additionally, $G_i^{\prime}(\tau_i; a_i) = 0 \implies r_i(\tau_i) > 0 \implies r_i^{\prime \prime} (\tau_i) < 0$ by the preceding Lemmas. So $G_i^{\prime}(\tau_i; a_i) = 0 \implies V_i^{\prime \prime}(\tau_i) < 0$. Now, note
$$
G_i^{\prime \prime}(\tau_i; a_i) = a_i V_i^{\prime \prime}(\tau_i) + \Pi_i^{\prime \prime}(\tau_i)
$$
Because $\ubar{a} < a_i$, the result follows immediately. 

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
qccv_tick <- qccv_tick + 1
qccv_qccv <- qccv_tick
```

**Lemma `r Lqccv`.`r qccv_qccv`:** $G_i^{\prime}(\tau_i; \ubar{a}) = 0 \implies G_i^{\prime \prime}(\tau_i; \ubar{a}) < 0$

**Proof:** Note that 
$$
\Pi_i^{\prime \prime}(\tau_i) = (\sigma - 1) \Pi_i^\prime(\tau_i) A(\tau_i) + (\sigma - 1) \Pi_i(\tau_i) A(\tau_i) B(\tau_i) + D(\tau_i)
$$
with
$$
\Pi_i^\prime(\tau_i) = (\sigma - 1) \Pi(\tau_i) A(\tau_i) + \frac{\Pi_i(\tau_i)}{I_i(\tau_i)} r_i^\prime(\tau_i)
$$
and 
$$
D(\tau_i) = \frac{\Pi_i(\tau_i)}{I_i(\tau_i)} r_i^{\prime \prime}(\tau_i) + r_i^\prime(\tau_i) \frac{\Pi_i(\tau_i)}{I_i(\tau_i)} \left( (\sigma - 1) A(\tau_i) \frac{r_i^\prime(\tau_i)}{I_i(\tau_i)} \right)
$$

Applying the derivations from the previous result,
\begin{align*}
G_i^{\prime \prime}(\tau_i; \ubar{a}) =& \ubar{a} V_i^{\prime \prime}(\tau_i) + \Pi_i^{\prime \prime}(\tau_i) \\
=& \ubar{a} k(\alpha) \left( P_i(\tau_i)^{-\alpha} r_i^{\prime \prime} (\tau_i) - \alpha A(\tau_i) \left( V_i(\tau_i) B(\tau_i) - \alpha V_i(\tau_i) A(\tau_i) \right) \right) + \\ 
& (\sigma - 1) \Pi_i^\prime(\tau_i) A(\tau_i) + (\sigma - 1) \Pi_i(\tau_i) A(\tau_i) B(\tau_i) + D(\tau_i) \\
=& \ubar{a} k(\alpha) \left( P_i(\tau_i)^{-\alpha} r_i^{\prime \prime} (\tau_i) - \Pi_i^\prime(\tau_i) B(\tau_i) + \alpha A(\tau_i) \Pi_i^\prime(\tau_i) \right) + \\
& (\sigma - 1) \Pi_i^\prime(\tau_i) A(\tau_i) + \Pi_i^\prime(\tau_i) B(\tau_i) + D(\tau_i) \\
=& \ubar{a} k(\alpha)  P_i(\tau_i)^{-\alpha} r_i^{\prime \prime} (\tau_i) + \ubar{a} k(\alpha) \Pi_i^\prime(\tau_i) \left( \alpha A(\tau_i) - B(\tau_i) \right) + \\
& \Pi_i^\prime(\tau_i) \left( (\sigma - 1) A(\tau_i) + B(\tau_i) \right) + D(\tau_i) \\
=& \ubar{a} k(\alpha)  P_i(\tau_i)^{-\alpha} r_i^{\prime \prime} (\tau_i) + \underbrace{(\sigma - 1) (p^{\alpha} (1 - p^{-1}))}_{=\beta < 1} \left( \alpha A(\tau_i) - B(\tau_i) \right) + \\
& \Pi_i^\prime(\tau_i) \left( (\sigma - 1) A(\tau_i) + B(\tau_i) \right) + D(\tau_i) \\
<& \ubar{a} k(\alpha)  P_i(\tau_i)^{-\alpha} r_i^{\prime \prime} (\tau_i) + \left( A(\tau_i) - B(\tau_i) \right) + \Pi_i^\prime(\tau_i) \left( (\sigma - 1) A(\tau_i) + B(\tau_i) \right) \\
=& \ubar{a} k(\alpha)  P_i(\tau_i)^{-\alpha} r_i^{\prime \prime} (\tau_i) + \Pi_i^\prime(\tau_i) \left( \sigma A(\tau_i) + B(\tau_i) \right) < 0
\end{align*}
$\blacksquare$

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
qccv_tick <- qccv_tick + 1
qccv_root <- qccv_tick
```

**Lemma `r Lqccv`.`r qccv_root`:** For all $a_i > \ubar{a}$,
$$
\evalat[\Big]{ \frac{\partial G_i(\tau_i; a_i)}{\partial \tau_i} }{\tau_i = 1} > 0
$$
and
$$
\lim_{\tau_i \rightarrow \infty} \frac{\partial G_i(\tau_i; a_i)}{\partial \tau_i} < 0
$$

**Proof:** Recall the first order condition in \ref{eq:Gfoc}. By construction, 
$$
\lim_{\tau_i \rightarrow \infty} \frac{\partial G_i}{\partial \tau_i} < 0
$$
for all $a_i > \ubar{a}$. 
$$
\evalat[\Big]{ \frac{\partial G_i}{\partial \tau_i} }{\tau_i=1} = \Pi_i^\prime(\tau_i) > 0
$$

$\blacksquare$

Lemmas `r Lqccv`.`r qccv_bound` and `r Lqccv`.`r qccv_qccv` imply that 
$$
0 > G_i^{\prime \prime}(\tau_i, \ubar{a}) > G_i^{\prime \prime}(\tau_i; a_i)
$$
whenever $G_i^\prime(\tau_i; a_i) = 0$. This guarantees that $G_i(\tau_i; a_i)$ is strictly quasiconcave for all $a_i > \ubar{a}$, ensuring that $\tau_i^\star(a_i)$ is unique. Lemma `r Lqccv`.`r qccv_root` ensures that $\tau_i^\star(a_i)$ is interior to $[1, \bar{\tau}]$. Note that the first order condition (\ref{eq:Gfoc}) does not depend on $\tau_j$, verifying the latter part of the claim. $\blacksquare$

