*TODO define constants*

The result follows from a series of Lemmas.

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
qccv_tick <- 1
qccv_rev <- qccv_tick
```

**Preliminaries:** Let
$$
A(\tau_i) = \left( 1 + \tau_i \right)^{-1} \tau_i^{-\sigma}
$$
$$
B(\tau_i) = (\sigma - 1) A(\tau_i) - \sigma \tau_i^{-1}
$$
and
$$
C(\tau_i) = \frac{1}{1 - r_i(\tau_i) / I_i(\tau_i)}
$$
where
$$
B^\prime(\tau_i) = (\sigma - 1) A(\tau_i) B(\tau_i) + \sigma \tau_i^{-2}
$$
$$
C^\prime(\tau_i) = C(\tau_i) r_i^\prime(\tau_i) I_i(\tau_i)^{-1}
$$

**Lemma `r Lqccv`.`r qccv_rev`:** $r_i^\prime(\tau_i) > 0 \implies r_i^{\prime \prime}(\tau_i) < 0$

**Proof:** Using the above quantities, we can write
$$
x_{ij}^{\star \prime}(\tau_i) = B(\tau_i) x_{ij}^\star(\tau_i) + \frac{x_{ij}^\star(\tau_i)}{I_i(\tau_i)} r_i^\prime(\tau_i)
$$
and 
\begin{align*}
r_i^\prime(\tau_i) &= (\tau_i - 1) p^\star x_{ij}^{\star \prime}(\tau_i) + p^\star x_{ij}^\star(\tau_i) \\
&= B(\tau_i) r_i(\tau_i) + \frac{r_i(\tau_i)}{I_i(\tau_i)} r_i^\prime(\tau_i) + p^\star x_{ij}^\star(\tau_i) \\
&= \frac{1}{1 - r_i(\tau_i) / I_i(\tau_i)} \left( B(\tau_i) r_i(\tau_i) + p^\star x_{ij}^\star(\tau_i) \right) \\
&= C(\tau_i) \left( B(\tau_i) r_i(\tau_i) + p^\star x_{ij}^\star(\tau_i) \right)
\end{align*}

Note that because $r_i(\tau_i) < I_i(\tau_i)$, $C(\tau_i)$ is positive and if $r_i^\prime(\tau_i) > 0$, then
\begin{equation} \label{eq:rprime1}
r_i(\tau_i) < - \frac{p^\star x_{ij}^\star(\tau_i)}{B(\tau_i)}
\end{equation}
Moreover, $C^\prime(\tau_i) \geq 0$ whenever $r^\prime(\tau_i) > 0$. 

Taking the second derivative and applying these facts about $C(\tau_i)$, we have
\begin{align*} 
r_i^{\prime \prime}(\tau_i) =& C^\prime(\tau_i) \left( B(\tau_i) r_i(\tau_i) + p^\star x_{ij}^\star(\tau_i) \right) + C(\tau_i) \left( B(\tau_i) r^\prime(\tau_i) + B^\prime(\tau_i) r_i(\tau_i) + p^\star x_{ij}^{\star \prime}(\tau_i) \right) \\
=& C^\prime(\tau_i) B(\tau_i) r_i(\tau_i) + C(\tau_i) \left( B(\tau_i) r^\prime(\tau_i) + B^\prime(\tau_i) r_i(\tau_i) + B(\tau_i) p^\star x_{ij}^\star(\tau_i) \right) + \\
& C^\prime(\tau_i) p^\star x_{ij}^\star(\tau_i) + C(\tau_i) p^\star x_{ij}^\star(\tau_i) I(\tau_i)^{-1} r_i^\prime(\tau_i) \\
=& C^\prime(\tau_i) B(\tau_i) r_i(\tau_i) + C(\tau_i) \left( B(\tau_i) r^\prime(\tau_i) + B^\prime(\tau_i) r_i(\tau_i) + B(\tau_i) p^\star x_{ij}^\star(\tau_i) \right) + \\
& 2 C(\tau_i) p^\star x_{ij}^\star(\tau_i) I(\tau_i)^{-1} r_i^\prime(\tau_i)
\end{align*}
whenever $r_i^\prime(\tau_i) > 0$.

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
qccv_tick <- qccv_tick + 1
qccv_rprime <- qccv_tick
```

**Lemma `r Lqccv`.`r qccv_rprime`:** $G_i^\prime(\tau_i; a_i) = 0 \implies r_i^{\prime}(\tau_i) > 0$

**Proof:**

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
qccv_tick <- qccv_tick + 1
qccv_bound <- qccv_tick
```

**Lemma `r Lqccv`.`r qccv_bound`:** $G_i^{\prime}(\tau_i; \ubar{a}) = 0$ and $G_i^{\prime}(\tau_i; a_i) = 0 \implies G_i^{\prime \prime}(\tau_i; \ubar{a}) > G_i^{\prime \prime}(\tau_i; a_i)$ for all $a_i > \ubar{a}$.

**Proof:**

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
qccv_tick <- qccv_tick + 1
qccv_qccv <- qccv_tick
```

**Lemma `r Lqccv`.`r qccv_qccv`:** $G_i^{\prime}(\tau_i; \ubar{a}) = 0 \implies G_i^{\prime \prime}(\tau_i; \ubar{a}) < 0$

**Proof:**

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
qccv_tick <- qccv_tick + 1
qccv_root <- qccv_tick
```

**Lemma `r Lqccv`.`r qccv_root`:** For all $a_i > \ubar{a}$,
$$
\evalat[\Big]{ \frac{\partial G_i(\tau_i; a_i)}{\partial \tau_i} }{\tau_i = 1} > 0
$$
and
$$
\lim_{\tau_i \rightarrow \infty} \frac{\partial G_i(\tau_i; a_i)}{\partial \tau_i} < 0
$$

**Proof:** Simplifying the derivative of the objective function gives
\begin{equation} \label{eq:Gfoc}
\begin{split}
\frac{\partial G_i}{\partial \tau_i} =& - a k(\alpha) P_i(\tau_i)^{-\alpha} p^{\sigma - 1} + a k(\alpha) P_i(\tau_i)^{-\alpha} \left( 1 + (\tau_i - 1) \left( (\sigma - 1) \chi(\tau_i) \tau_i^{-\sigma} - \sigma \tau_i^{-1} \right) \right) + \\
& (\sigma - 1) \chi_i(\tau_i)
\end{split}
\end{equation}

It is straightforward to verify that for all $a_i > \ubar{a}$,
$$
\evalat[\Big]{ \frac{\partial G_i}{\partial \tau_i} }{\tau_i=1} > 0
$$
and
$$
\lim_{\tau_i \rightarrow \infty} \frac{\partial G_i}{\partial \tau_i} < 0
$$
$\blacksquare$

Lemmas `r Lqccv`.`r qccv_bound` and `r Lqccv`.`r qccv_qccv` imply that 
$$
0 > G_i^{\prime \prime}(\tau_i, \ubar{a}) > G_i^{\prime \prime}(\tau_i; a_i)
$$
whenever $G_i^\prime(\tau_i; a_i) = 0$. This guarantees that $G_i(\tau_i; a_i)$ is strictly quasiconcave for all $a_i > \ubar{a}$, ensuring that $\tau_i^\star(a_i)$ is unique. Lemma `r Lqccv`.`r qccv_root` ensures that $\tau_i^\star(a_i)$ is interior to $[1, \bar{\tau}]$. Note that the first order condition (\ref{eq:Gfoc}) does not depend on $\tau_j$, verifying the latter part of the claim. $\blacksquare$

